Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-07-02 Papers/ms.tex
Para about computational cost

>>>>

We generated 5,000 samples from the DNest target distribution and thinned
by a factor of $10^5$, so $5 \times 10^8$ MCMC iterations were actually
performed, taking approximately 36 hours. After resampling, this resulted in 805
equally weighted posterior samples. Although this image is smaller than the
simulated data ($46 \times 46$ pixels), we fired $2 \times 2$ rays per pixel
for greater accuracy.
